---
title: "R Notebook"
output: html_notebook
---


```{r}
## This notebook contains codes for running 1-year empirical studies of Bayesian Estimation and Optimization.

## Bayes Opt being considered here use EIVar as acquisition function and with time series adjustment. (i.e. AdjBO-EIVar proposed in paper)
## For other variations of BO, need to modify 'LPO_BO_NoisyOptimizer.R' and 'LPO_BO_TestEvaluation.R'.

## Bayes Estimate being considered here includes 3 model: Bayes-Stein estimate, Bayes estimate based on belief in asset pricing model, and Bayesian averaging estimate
```


```{r}
# Import dependencies
source('LPO_SampleEstimation.R')
source('LPO_BayesEstimation.R')
source('LPO_CV.R')
source('LPO_CV_TestEvaluation.R')
source('LPO_BO_NoisyOptimizer.R')
source('LPO_BO_TestEvaluation.R')
source('LPO_TrueLambdaBacktest.R')
```


```{r}
# Read data
data<-read.csv("sp500data.csv",header=TRUE)
sp500con<-read.csv("sp500con.csv",header=TRUE)
mdata<-matrix(unlist(data),nrow=nrow(data),ncol=ncol(data)) #Adjusted Close Prices of the securities
fulltickerlabel<-as.vector(unlist(read.csv("sp500data.csv",header=FALSE)[1,])[-1])
compind<-complete.cases(t(data));compind[1]=FALSE
comptickerlabel<-fulltickerlabel[compind[-1]]

# For Bayes Averaging
# data = data[-(1:231),]
# mdata<-matrix(unlist(data),nrow=nrow(data),ncol=ncol(data)) #Adjusted Close Prices of the securities
```


```{r}
S<-mdata[,compind]
p0=ncol(S);n0=nrow(S)
#Return matrix
R<-matrix(0,nrow=n0-1,ncol=p0)
for(i in 2:n0){for(j in 1:p0){R[i-1,j]=(S[i,j]-S[i-1,j])/S[i-1,j]}}
```


```{r}
# Read Fama-French 3 factor model data 
df_ff3 = read.csv("FF3-0317.csv", stringsAsFactors=FALSE)
df_ff3$Date = as.Date(df_ff3$Date, format = "%m/%d/%Y")
df_ff3$Mkt.RF = df_ff3$Mkt.RF / 100
df_ff3$SMB = df_ff3$SMB / 100
df_ff3$HML = df_ff3$HML / 100
```


```{r}
# Pick subset of data to evaluate performance
df_ff3_eval = df_ff3[df_ff3['Date']>='2013-01-01' & df_ff3['Date']<='2014-12-31' ,]
df_ff3_eval = df_ff3_eval[-1,]
ff3mat = as.matrix(df_ff3_eval[,-c(1,5)])
nrow(ff3mat)
ncol(ff3mat)
```


```{r}
#sink()
```



#####################
# See LPO_TrueLambdaBacktest.R
# Find true optimal lambda by incorporating future asset prices.
# For LPO with Sample, Bayes-Stein, Bayes Asset Pricing and Bayes Averaging estimate.

# True lambda LPO Bayes-Stein
```{r}
truelambda.l1fastbs = TrueOptimalLambda.lpobs(r=R, n.train=251,n.test=252,
                                              delta=rep(1,ncol(R)), step=1/252,
                                              shrinkage= TRUE, normalized = TRUE, nlambda=30)
```

# True lambda LPO Bayes asset pricing
```{r}
truelambda.l1fastff3 = TrueOptimalLambda.lpoassetp(r=R, f=ff3mat,sigma_alpha=0.01,
                                                   nu=500,n.train=251,
                                                   n.test=252,
                                                   delta=rep(1,ncol(R)),
                                                   step=1/252,normalized=TRUE, nlambda=30)
```

# True lambda LPO Bayes averaging
```{r}
# Note: Change matrix of returns R first (see commented block above)
truelambda.l1fastbayesave = TrueOptimalLambda.lpobayesave(r=R, random.subset = TRUE,
                                                          n.test= 19+252,
                                                          delta=rep(1,ncol(R)),
                                                          step=1/252,
                                                          normalized=TRUE, nlambda=30)
```

#####################
# See LPO_BO_TestEvaluation.R
# Evaluate out-of-sample performance of Bayes Opt (BO) when tuning LPO with Sample, Bayes-Stein, Bayes Asset Pricing and Bayes Averaging estimate.

# LPO with Sample estimate - tuned with Bayes opt
```{r}
testResults.lposamplebayesopt = bayesopt.eval.l1fast(r=R, random.start = FALSE, 
                                                     n.train = 251, n.test=252,
                                                     delta=rep(1,ncol(R)), step=1/252,
                                                     normalized = TRUE)
```


# LPO with Bayes Stein estimate - tuned with Bayes opt
```{r}
testResults.lpobsbayesopt = bayesopt.eval.l1fastbayesstein(r=R, random.start = FALSE,
                                                           n.train = 251, n.test=252,
                                                           delta=rep(1,ncol(R)), step=1/252,
                                                           shrinkage = TRUE, normalized = TRUE)

```


# LPO with Bayes estimate based on belief in asset pricing model (FF3) - tuned with Bayes opt
```{r}
testResults.lpoff3bayesopt = bayesopt.eval.l1fastbayesassetp(r=R, f=ff3mat,
                                                             sigma_alpha=0.01,
                                                             nu=500,n.train=251,
                                                             n.test=252,
                                                             delta=rep(1,ncol(R)),
                                                             step=1/252,normalized=TRUE)

```


# LPO with Bayes Averaging estimate - tuned with Bayes opt
```{r}
# Note: Change matrix of returns R first (see commented block above)
testResults.lpoavebayesopt = bayesopt.eval.l1fastbayesave(r=R,random.subset = TRUE,
                                                          n.test= 19+252,
                                                          delta=rep(1,ncol(R)),
                                                          step=1/252,
                                                          normalized=TRUE, lambda=NULL)

```


#####################
# Evaluate out of sample performance of cross-validation (CV) when tuning LPO with Sample, Bayes-Stein, Bayes Asset Pricing and Bayes Averaging estimate.

# LPO with Sample estimate - tuned with CV
```{r}
testResults.lpo = negSR.eval.l1fast(R,n.train=251,n.test=252,delta=rep(1,ncol(R)),step=1/252, normalized = TRUE)
```

# LPO with Bayes-Stein estimate - tuned with CV
```{r}
testResults.lpobscv = negSR.eval.l1fastbayesstein(R,n.train=251, n.test=20,
                                                        delta=rep(1,ncol(R)),step=1/252,
                                                        shrinkage = TRUE, normalized=TRUE)
```

# LPO with  Bayes estimate based on belief in asset pricing model (FF3) - tuned with CV
```{r}
testResults.lpoassetpcv = negSR.eval.l1fastbayesassetpricing(R,ff3mat,
                                                                         sigma_alpha=0.01,
                                                                         nu=500,n.train=251,
                                                                         n.test=20,
                                                                         delta=rep(1,ncol(R)),
                                                                         step=1/252,normalized=TRUE )
```


# LPO with  Bayes Averaging estimate - tuned with CV
```{r}
# Note: Change matrix of returns R first (see commented block above)
testResults.lpoavecv = negSR.eval.l1fastbayesaveraging(R, random.subset = TRUE,
                                                                n.test= 19+252,
                                                                delta=rep(1,ncol(R)),
                                                                step=1/252,
                                                                normalized=TRUE, lambda=NULL)
```


#####################
# Other strategies for benchmark
# Equally-weighted
```{r}
EWtestresults = negSR.eval.EW(R, n.train = 251, n.test = 252)
```

# Plug in
```{r}
pluginresults = eval.plugin(R, n.train = 251, n.test = 252, step=1/252)
```

